### 2023-04-08 output/group_3_crimes_50m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -0.91 & 1.00 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,927.86 & 0.03 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 706.17 & 0.11 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 2.07 & 0.22 & 0.07 & -0.01 & 0.31 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_3_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_3_crimes_50m & 0.00 & 0.11 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.44 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.74 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.15 & 0.00 \\
 & no_cause & 0.57 & 0.95 \\
 & non_payment & 0.35 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
 & hasAttyP & 0.61 & 0.00 \\
 & isEntityD & 0.70 & 0.06 \\
 & isEntityP & 0.58 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.00 & 0.07 \\
 & pre_treatment_change_in_group_3_crimes_50m & 0.51 & 0.87 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.18 & 0.22 \\
 & job_density_2013 & 0.32 & 0.10 \\
 & med_hhinc2016 & 0.28 & 0.05 \\
 & poor_share2010 & 0.22 & 0.96 \\
 & popdensity2010 & 0.22 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.29 & 0.00 \\
 & no_cause & 0.35 & 0.95 \\
 & non_payment & 0.14 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.63 & 0.00 \\
 & hasAttyP & 0.68 & 0.00 \\
 & isEntityD & 0.33 & 0.06 \\
 & isEntityP & 0.78 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_4_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.87 \\
 & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.67 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
 & no_cause & 0.28 & 0.95 \\
 & non_payment & 0.09 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
 & hasAttyP & 0.07 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.11 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_1000m & 0.00 & 0.05 \\
 & pre_treatment_change_in_group_4_crimes_1000m & 0.00 & 0.41 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.01 & 0.00 \\
 & no_cause & 0.00 & 0.95 \\
 & non_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.00 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_4_crimes_100m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_4_crimes_100m & 0.06 & 0.02 & 0.01 & -0.00 & 0.88 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_100m & 7.78 & 0.18 & 0.79 & -0.09 & 0.90 \\
 & pre_treatment_change_in_group_4_crimes_100m & -0.03 & -0.02 & 0.49 & 0.00 & 0.99 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.65 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -180.58 & 0.91 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -529.96 & 0.55 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.56 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -251.53 & 0.58 \\
\cline{1-7}
\textit{Panel C} & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.46 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & -0.00 & 0.93 \\
 & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.36 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.96 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.44 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_4_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_100m & 0.37 & 0.64 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.11 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.05 & 0.00 \\
 & no_cause & 0.37 & 0.95 \\
 & non_payment & 0.02 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.71 & 0.00 \\
 & hasAttyP & 0.78 & 0.00 \\
 & isEntityD & 0.29 & 0.06 \\
 & isEntityP & 0.04 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.79 \\
 & pre_treatment_change_in_group_4_crimes_100m & 0.00 & 0.49 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.30 & 0.00 \\
 & no_cause & 0.06 & 0.95 \\
 & non_payment & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.04 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
 & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
 & no_cause & 0.67 & 0.95 \\
 & non_payment & 0.28 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
 & hasAttyP & 0.51 & 0.00 \\
 & isEntityD & 0.28 & 0.06 \\
 & isEntityP & 0.92 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.27 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.08 & 0.00 \\
 & no_cause & 0.00 & 0.95 \\
 & non_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.26 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.06 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_4_crimes_50m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_4_crimes_50m & 0.02 & 0.01 & 0.01 & -0.00 & 0.43 \\
\cline{1-7}
\textit{Panel B} & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 757.12 & 0.37 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_50m & 1.77 & -0.10 & 0.54 & -0.05 & 0.77 \\
 & pre_treatment_change_in_group_4_crimes_50m & 0.01 & 0.01 & 0.48 & 0.00 & 1.00 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.26 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -391.41 & 0.79 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -578.94 & 0.11 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.89 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.02 & 0.04 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_4_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_50m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_50m & 0.99 & 0.17 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.28 & 0.22 \\
 & job_density_2013 & 0.40 & 0.10 \\
 & med_hhinc2016 & 0.03 & 0.05 \\
 & poor_share2010 & 0.06 & 0.96 \\
 & popdensity2010 & 0.43 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.82 & 0.00 \\
 & no_cause & 0.90 & 0.95 \\
 & non_payment & 0.78 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.86 & 0.00 \\
 & hasAttyP & 0.84 & 0.00 \\
 & isEntityD & 0.93 & 0.06 \\
 & isEntityP & 0.80 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_50m & 0.00 & 0.54 \\
 & pre_treatment_change_in_group_4_crimes_50m & 0.01 & 0.48 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.65 & 0.05 \\
 & poor_share2010 & 0.33 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.67 & 0.00 \\
 & no_cause & 0.09 & 0.95 \\
 & non_payment & 0.16 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.45 & 0.00 \\
 & hasAttyP & 0.13 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.02 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_5_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_500m & 0.00 & 0.87 \\
 & pre_treatment_change_in_group_2_crimes_500m & 0.00 & 0.67 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.22 & 0.00 \\
 & no_cause & 0.28 & 0.95 \\
 & non_payment & 0.09 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.84 & 0.00 \\
 & hasAttyP & 0.07 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.11 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_1000m & 0.00 & 0.76 \\
 & pre_treatment_change_in_group_5_crimes_1000m & 0.00 & 0.90 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
 & no_cause & 0.01 & 0.95 \\
 & non_payment & 0.01 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.95 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_1000m & 0.00 & 0.76 \\
 & pre_treatment_change_in_group_5_crimes_1000m & 0.00 & 0.90 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.00 \\
 & no_cause & 0.01 & 0.95 \\
 & non_payment & 0.01 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.95 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_5_crimes_500m & 0.00 & 0.37 \\
 & pre_treatment_change_in_group_5_crimes_500m & 0.00 & 0.05 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
 & no_cause & 0.03 & 0.95 \\
 & non_payment & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.61 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_5_crimes_50m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_5_crimes_100m & 3.87 & 0.18 & 0.24 & -0.05 & 0.75 \\
 & pre_treatment_change_in_group_5_crimes_100m & 0.01 & -0.01 & 0.52 & -0.00 & 0.98 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.60 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -159.16 & 0.91 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -261.65 & 0.45 \\
\cline{1-7}
\textit{Panel D} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.01 & 0.21 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_5_crimes_50m & 1.13 & 0.03 & 0.69 & 0.04 & 0.55 \\
 & pre_treatment_change_in_group_5_crimes_50m & 0.01 & -0.00 & 0.72 & 0.00 & 0.71 \\
\cline{1-7}
\textit{Panel B} & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 88.93 & 0.51 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_6_crimes_1000m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_1000m & 3.40 & 0.30 & 0.00 & -0.01 & 0.93 \\
 & pre_treatment_change_in_group_4_crimes_1000m & 0.17 & -0.05 & 0.03 & -0.00 & 0.98 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.92 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -34.03 & 0.98 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -110.46 & 0.90 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.90 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -51.28 & 0.91 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.83 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.99 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.00 & 0.85 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_6_crimes_1000m & 202.74 & 9.39 & 0.02 & -0.38 & 0.92 \\
 & pre_treatment_change_in_group_6_crimes_1000m & -2.85 & -0.09 & 0.60 & 0.00 & 0.98 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.94 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -49.22 & 0.97 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -87.71 & 0.92 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.94 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -47.77 & 0.92 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel C}} & for_cause & 0.17 & 0.08 & 0.00 & -0.00 & 0.92 \\
 & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.99 \\
 & non_payment & 0.77 & -0.08 & 0.00 & -0.00 & 0.97 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & -0.00 & 0.93 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.99 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.00 & 0.96 \\
\cline{1-7}
\bottomrule
\end{tabular}
